\documentclass[fleqn]{exam}
\usepackage{chemfig}
\usepackage{amssymb}

\begin{document}

\begin{questions}
  \setcounter{question}{19}
  \question
  How can collision theory explain the effect of surface area on reaction rate?
  \vspace{1in}
  \question
  The following reaction is taking place at a very slow rate in a closed container at room temperature.
  \schemestart
  S(s) \+ \chemfig{O_2} \arrow{->} \chemfig{SO_2}(g)
  \schemestop
  State the effect of the following procedures on the rate of this reaction and explain the effect in terms
  of collision theory.\newline
  (a) The temperature is decreased.\newline
  (b) More \chemfig{0_2}(g) is added to the same volume.\newline
  (c) Some \chemfig{SO_2}(g) is removed.\newline
  (d) The sulphur is ground up into a powder.\newline
  (e) The volume of the container is increased.\newline

  \vspace{1in}
  \question
  Explain in terms of collision theory why kindling is used to start a fire, rather than a large block of wood.
  \vspace{1in}
  \question
  When breaking the Br-Br bond in \chemfig{Br_2}, what happens to the potential energy of the molecule?
  \vspace{1in}
  \question
  $\Delta$H =-25 kJ for the reaction: A $\rightarrow$ B. Re-write this equation to show the 25 kJ properly on reactant or product side. Draw a graph of "enthalpy" versus "reaction proceeds, showing the relative enthalpies of the reactant and product, and the enthalpy change. Will the surroundings feel warmer or cooler as the reaction occurs?
  \vspace{1in}
  \newpage
  \question
  If a reaction absorbs 40 kJ of heat, what is $\Delta$H for the reaction?
  \vspace{1in}
  \question
  What is $\Delta$H for the reaction C + 30 kJ $\rightarrow$ D? Which have more energy, reactants or products?
  Draw a graph of "enthalpy' versus "reaction proceeds", showing the relative enthalpies of the
  reactant and product, and the enthalpy change. Will the surroundings feel warmer or cooler as
  the reaction occurs?
  \vspace{1in}
  \question
  Draw a graph of "enthalpy" versus "reaction proceeds" for a reaction in which R $\rightarrow$ P + 10 kJ.
  Will the surroundings feel warmer or cooler as the reaction occurs?
  \vspace{1in}
  \question
  When one mole of HCl reacts with one mole of NaOH to produce one mole of NaCl and one mole
  of \chemfig{H_2O}, 59 kJ of heat is absorbed by the surroundings. Draw a graph of enthalpy" versus
  "reaction proceeds", showing the relative enthalpies of reactant and product, and the enthalpy change.


\end{questions}

\end{document}
