\documentclass[fleqn]{exam}
\usepackage{chemfig}
\usepackage{siunitx}

\begin{document}

\begin{questions}

  \setcounter{question}{33}


  \question A cell is made up as follows. A piece of Ni foll is immersed in a beaker of \chemfig{NiCl_2} solution, and a strip of Cu toil is immersed in a beaker of \chemfig{CuSO_4} solution. The metal electrodes are connected by a wire and the beakers connected by a salt bridge. The net ionic equation for the reaction is: \newline
  \schemestart \chemfig{Ni+ Cu^{2+}} \arrow{->} \chemfig{Ni^{2+}} + Cu \schemestop
  \begin{parts}
    \part Which electrode is the anode?
    \vspace{1in}
    \part Toward which electrode do the \chemfig{SO^{2-}_4} ions migrate?
    \vspace{1in}
    \part Which way do the electrons flow in the wire?
    \vspace{1in}
    \part If 0.025 mol of Cu(s) is produced in the reaction, how many moles of electrons flow through the wire?
    \vspace{1in}
    \part Toward which electrode do the \chemfig{Ni^{2+}} ions migrate after being formed?
  \end{parts}

  \newpage

  \question An electrochemical cell is made by placing a weighed strip of Sn in a beaker containing 1 M \chemfig{SnSO_4} and a weighed strip of Ag in a beaker containing 1 M \chemfig{AgNO_3}. The metal strips are connected by a wire and the beakers are connected by a salt bridge. After several hours the Sn electrode decreases in mass.
  \begin{parts}
    \part What is the net ionic equation for the reaction?
    \vspace{.8in}
    \part Which electrode is the cathode?
    \vspace{.8in}
    \part Toward which electrode do the \chemfig{Ag^+} ions migrate?
    \vspace{.8in}
    \part Which way do the electrons flow in the wire?
    \vspace{.8in}
    \part Does the Ag electrode gain or lose mass?
    \vspace{.8in}
    \part If 0.010 mol of Sn(s) goes into solution, how many moles of electrons flow through the wire?
    \vspace{.8in}
    \part If 0.020 mol of Sn goes into solution, how many moles of Ag are involved in the reaction?
    \vspace{.8in}
    \part How many moles of electrons flow through the salt bridge in part (g)?
  \end{parts}

\end{questions}

\end{document}
